### 2012-11-22 inst/examples/mult_uncertainty_test.Rmd
A few small tweaks to probability calculations
Handle the case of mu = grid zero, not just exactly zero, to avoid introducing NAs

Calculate dlnorm as (x_grid/mu, 0, sigma), rather than as (x_grid, mu, sigma).

Transpose of measurement error in M %*% F.  Because now we want to treat x as given, integrate over range of y?  (no, probably not?)

standardize noise level between old and g

    sigma_g <- sigmas['sigma_g']      
    sigma_m <- sigmas['sigma_m']
    sigma_i <- sigmas['sigma_i']
    n_x <- length(x_grid)
    n_h <- length(h_grid)
    D <- matrix(NA, nrow=n_x, ncol=Tmax)

@@

    # integrate over uncertainty in I and X 
    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
        if(mu==0)
          out[1] <- 1   
        else {
         out <- pdfn(x_grid, mu, sigma_g)
         if(sum(out) == 0)
           out[1] = 1
         out
        }
        out/sum(out)
      }))
    })

    Ep <- M %*% P %*% t(I)
    V <- Ep
    for(t in 1:Tmax){
      D[,(Tmax-t+1)] <- apply(V, 1, which.max)
      v_t <- apply(V, 1, max) # vector of current values
      V <- sapply(1:n_h, function(j){ # updated value matrix
        Ep[,j] + (1-delta) * M %*% F[[j]] %*% v_t
      })
    }
    list(D=D, M=M, I=I, P=P, Ep=Ep, V=V, F=F)
}

@@

``` {r stateeq}
f <- function(x, h, p){
  A <- p[1] 
  B <- p[2] 
  s <- pmax(x-h, 0)
  A * s/(1 + B * s)
}
profit = function(x,h) pmin(x, h)

pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
xmin <- 0
xmax <- 1.5 * K
n_x <- 200
n_h <- n_x
x_grid <- seq(xmin, xmax, length = n_x)  
h_grid <- seq(xmin, xmax, length = n_h)
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- 0.5
````

@@

```{r}
# Uniform pdf where width scales with mean (probably better way to do that)
# And handles degenerate/delta fn cases such as no width and zero mean
FUN <- function(P, mu, s){
  if(mu == 0){
    as.integer(P == 0)
  } else if(s > 0){
    if(mu > 0) dunif(P, mu * (1 - s), mu * (1 + s))
  }
  else { # delta spike
    P <- snap_to_grid(P, x_grid)
    mu <- snap_to_grid(mu, x_grid)
    as.integer(P == mu)
  }
}
pdfn <- Vectorize(FUN)
```

```{r mult_uncertainty}
out <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0.3, sigma_i=0.3), pdfn=pdfn)  
```

```{r noisetypes}
new <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0, sigma_i=0), pdfn=pdfn)  
m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0.3, sigma_i=0), pdfn=pdfn)  
i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0, sigma_i=0.3), pdfn=pdfn)  
```

@@

```{r policyfn_data}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, old = x_grid[opt$D[,1]], new = x_grid[new$D[,1]], meas = x_grid[m$D[,1]], imp = x_grid[i$D[,1]]), id="stock")
```

>>>>

# sigmas = c(0.2, 0.2, .0)
    sigma_g <- sigmas[1]      
    sigma_m <- sigmas[2]
    sigma_i <- sigmas[3]
    n_x <- length(x_grid)
    n_h <- length(h_grid)
    D <- matrix(NA, nrow=n_x, ncol=Tmax)

@@

    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
        # Handle special cases
        if(snap_to_grid(mu,x_grid)==0){
          out[1] <- 1   
        } else {
         out <- pdfn(x_grid, mu, sigma_g)
        }
        out/sum(out)
      }))
    })

    # n_y by n_x, given y %*% n_x by n_h %*% n_h by n_q, given q
    Ep <- M %*% P %*% t(I)
    V <- Ep
    for(t in 1:Tmax){
      D[,(Tmax-t+1)] <- apply(V, 1, which.max) 
      ## q can often exceed y, if fishing is free, there might be more x than you think.  
      #if(any(pmin(D[,(Tmax-t+1)], 1:n_h) !=  D[,(Tmax-t+1)])) stop()
      #v_t <- sapply(1:n_h, function(i) V[i,D[i,(Tmax-t+1)]]) # Look-up value given by which.max
      v_t <- apply(V, 1, max) # vector of current values 
      V <- sapply(1:n_h, function(j){ # updated value matrix
        Ep[,j] + (1-delta) * t(M) %*% F[[j]] %*% v_t
      })
    }
    list(D=D, M=M, I=I, P=P, Ep=Ep, V=V, F=F)
}

@@

``` {r stateeq}
f <- function(x, h, p){
  A <- p[1] 
  B <- p[2] 
  s <- pmax(x-h, 0)
  A * s/(1 + B * s)
}
profit = function(x,h) pmin(x, h)
#profit <- profit_harvest(price=1, c0 = 0, c1=0)

pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
xmin <- 0
xmax <- 1.5 * K
n_x <- 100
n_h <- n_x
x_grid <- seq(xmin, xmax, length = n_x)  
h_grid <- seq(xmin, xmax, length = n_h)
delta <- 0.05
xT <- 0
OptTime <- 25

sigma_g=0.1
````

@@

```{r}
# Uniform pdf where width scales with mean (probably better way to do that)
# And handles degenerate/delta fn cases such as no width and zero mean
FUN <- function(P, mu, s){
  if(mu == 0){
    as.integer(P == 0)
  } else if(s > 0){
    if(mu > 0){
      dlnorm(P/mu, 0, s)
      #dunif(P, mu * (1 - s), mu * (1 + s))
    }
  }
  else { # delta spike
    P <- snap_to_grid(P, x_grid)
    mu <- snap_to_grid(mu, x_grid)
    as.numeric(as.integer(P == mu))
  }
}
pdfn <- Vectorize(FUN)
```

```{r noisetypes}
g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0), pdfn=pdfn)  
m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0.1, sigma_i=0), pdfn=pdfn)  
i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0, sigma_i=0.1), pdfn=pdfn)  
```

@@

```{r policyfn_data}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, old = x_grid[opt$D[,1]], g = x_grid[g$D[,1]], meas = x_grid[m$D[,1]], imp = x_grid[i$D[,1]]), id="stock")
```
